Analysis of Fault Localization Techniques on REST APIs

### 2024-05-15 CS563-Project/Paper/paper.tex
Added the Spreadsheet for bugs which might be better for our project

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xcolor}
\newcommand{\todo}[1]{\textcolor{red}{{\bfseries [[#1]]}}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\subsection{Problem statement}
    REST APIs (Representational State Transfer) have become backbone of the modern web and cloud applications. They facilitate seamless interactions between client and server through stateless communication, enabling services to be scalable, reliable, and easily integrateable. Basically, REST APIs are a set of rules and standards used to enable communication between different software applications over the internet. They are built around the use of standard HTTP methods such as GET, POST, PUT, and DELETE to interact with resources, which are any kind of data or service that can be named on a network.
    Given their critical role, the effective identification and resolution of faults within REST APIs remain a significant challenge, prompting the need for research on how fault localization techniques work to their unique structure and functionality.

@@

\subsection{Motivation}
    As systems that rely on REST APIs grow in scale and complexity, minor faults can escalate into major disruptions, impacting user experience and business operations. 
    This research is motivated by the need to evaluate how well current fault localization techniques perform in the unique context of REST APIs. 
    The goal is to determine if these techniques can indeed be applied effectively to REST APIs and, if so, to explore which types of faults are more amenable to being localized. 
    This understanding could potentially allow developers to more efficiently diagnose and address issues, thereby enhancing the stability and performance of REST API-based systems.

@@

\subsection{Relation with software engineering research}

@@

\subsection{Key Insight or Idea}
    The primary objective of this research is to evaluate the effectiveness of existing fault localization techniques within the unique context of REST APIs, which feature a mix of code and non-code artifacts. 
    This study will systematically apply established fault localization methods—Spectrum-Based Fault Localization (SBFL), Information Retrieval Fault Localization (IRFL), and Program Slicing—to a self-created dataset of REST API faults. 
    This dataset will be meticulously developed to represent a wide range of faults typical in REST APIs and classified according to an existing comprehensive taxonomy derived from previous research.

@@

\subsection{Assumptions}
    \begin{itemize}
        \item \textit{Assumption 1:} It is assumed that the faults in the dataset are correctly classified according to the existing comprehensive taxonomy.
        \item \textit{Assumption 2:} Assume that the selected fault localization techniques are suitable for application to REST APIs, despite their original design for conventional software systems. This includes the assumption that these techniques can handle the unique challenges posed by REST APIs, such as dealing with non-code artifacts.
    \end{itemize}

@@

\subsection{Research questions}
    The primary research questions are formulated as follows:
    \begin{itemize}
        \item \textbf{RQ1:} What categories of faults (as per the existing taxonomy) are most effectively localized by current techniques?
        \item \textbf{RQ2:} Which fault localization techniques offer the highest accuracy and precision in the context of REST APIs?
    \end{itemize}
    % \todo{What research question(s) will you answer?}

\subsection{Evaluation Dataset}

\subsection{Evaluation metrics}

@@

\section{Related Work}
\label{sec:relatedwork}
% \todo{R2Fix~\cite{Liu13} and iFixR~\cite{Koyuncu19}, use information retrieval-based fault localization~(IRFL)
% that ranks suspicious program statements based on their similarity with bug reports.}

@@

@@

@@

@@

@@

% \bibliographystyle{IEEEtran}
% \bibliography{relatedwork}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{tabularx}

\newcommand{\todo}[1]{\textcolor{red}{{\bfseries [[#1]]}}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

% \subsection{Problem statement}
    REST APIs (Representational State Transfer) have become backbone of the modern web and cloud applications. They facilitate seamless interactions between client and server through stateless communication, enabling services to be scalable, reliable, and easily integrateable ~\cite{li2016} ~\cite{neumann2018}. Basically, REST APIs are a set of rules and standards  defined by OpenAPI ~\cite{ed-douibi2018} used to enable communication between different software applications over the internet. They are built around the use of standard HTTP methods such as GET, POST, PUT, and DELETE to interact with resources, which are any kind of data or service that can be named on a network.
    Given their critical role, the effective identification and resolution of faults within REST APIs remain a significant challenge ~\cite{barbir2007}, prompting the need for research on how fault localization techniques work to their unique structure and functionality.

@@

% \subsection{Motivation}
    As systems that rely on REST APIs grow in scale and complexity ~\cite{khare2004}, minor faults can escalate into major disruptions, impacting user experience and business operations. 
    This research is motivated by the need to evaluate how well current fault localization techniques perform in the unique context of REST APIs. 
    The goal is to determine if these techniques can indeed be applied effectively to REST APIs and, if so, to explore which types of faults are more amenable to being localized. 
    This understanding could potentially allow developers to more efficiently diagnose and address issues, thereby enhancing the stability and performance of REST API-based systems.

@@

% \subsection{Relation with software engineering research}

@@

% \subsection{Key Insight or Idea}
    The primary objective of this research is to evaluate the effectiveness of existing fault localization techniques within the unique context of REST APIs, which feature a mix of code and non-code artifacts. 
    This study will systematically apply established fault localization methods—Spectrum-Based Fault Localization (SBFL), Information Retrieval Fault Localization (IRFL), and Program Slicing—to a self-created dataset of REST API faults. 
    This dataset will be meticulously developed to represent a wide range of faults typical in REST APIs and classified according to an existing comprehensive taxonomy derived from previous research.

@@

% \subsection{Assumptions}
    Our assumptions:
    \begin{itemize}
        \item \textit{Assumption 1:} It is assumed that the faults in the dataset are correctly classified according to the existing comprehensive taxonomy ~\cite{automatedTestTaxonomy} .
        \item \textit{Assumption 2:} Assume that the selected fault localization techniques are suitable for application to REST APIs, despite their original design for conventional software systems. This includes the assumption that these techniques can handle the unique challenges posed by REST APIs, such as dealing with non-code artifacts.
    \end{itemize}

@@

% \subsection{Research questions}
    The primary research questions are formulated as follows:
    \begin{itemize}
        \item \textbf{RQ1:} What categories of faults (as per the existing taxonomy) are most effectively localized by current techniques?
        \item \textbf{RQ2:} Which fault localization techniques offer the highest accuracy and precision in the context of REST APIs?
    \end{itemize}
    % \todo{What research question(s) will you answer?}

% \subsection{Evaluation Dataset}
For the evaluation dataset, we will mine bugs and their fixes from REST API projects that utilize Spring Boot or Jersey frameworks. 
This dataset will encompass various categories of faults identified in REST APIs. By analyzing repositories and commit histories, we will extract specific instances where bugs have been documented and subsequently fixed. 
The categorization of these faults will be categorized with an established taxonomy of API faults ~\cite{automatedTestTaxonomy} , ensuring that each bug is classified according to its nature and impact. This rigorous dataset compilation aims to provide a comprehensive basis for testing fault localization techniques within a controlled, relevant environment.

% \subsection{Evaluation metrics}
For evaluation of fault localization techniques using the dataset derived from REST APIs employing Spring Boot and Jersey frameworks will be measured by Top-k accuracy, and EXAM score.
These metrics will collectively provide a thorough assessment of each fault localization technique's ability to detect and accurately categorize faults in REST APIs, contributing to a detailed understanding of their practical utility and areas for improvement.

@@

\section{Related Work}
\label{sec:relatedwork}

Fault localization techniques have long been an integral part of software maintenance, aiding developers by pinpointing the origins of failures within software systems. 
A variety of approaches have been explored ~\cite{Wong2023_Software_Fault_localization}, including Information Retrieval (IR) based methods, Spectrum-Based Fault Localization (SFL), and more comprehensive software engineering tools.

Information Retrieval Based Fault Localization: The work by Klaus Changsun Youm et al introduces an advanced IR-based fault localization method called BLIA, which integrates bug reports and code change history to enhance the localization process  ~\cite{7467300} ~\cite{ctx114059874780001451}. BLIA notably improves the accuracy of locating bugs by analyzing texts, stack traces, and comments within bug reports alongside source file structures and version histories. This method has shown significant improvements over previous tools such as BugLocator and BLUiR, particularly at the file and method levels, by refining the granularity of localization results. This approach underscores the potential of IR-based methods in handling complex software systems, aligning with the need to explore such techniques within REST API environments.

The Jaguar tool, described by Ribeiro et al, utilizes SBFL technique to identify faulty code excerpts in Java programs ~\cite{8367068}. By employing both control-flow and data-flow spectra and integrating the lightweight ba-dua coverage tool, Jaguar efficiently supports the analysis of large programs. The capability of Jaguar to provide detailed visualizations of suspicious program elements highlights the effectiveness of SFL in traditional software environments. The distinction between data-flow and control-flow spectra offers a nuanced view of fault localization that could be pertinent to analyzing REST APIs, known for their complex interactions and stateless operations.

Debugging in IDEs, particularly using tools like Visual Studio Code for web applications, illustrates the practical aspects of fault localization in real-world scenarios ~\cite{DebuggingCode}. The capabilities of IDEs to facilitate debugging through breakpoints and variable inspections are directly relevant to the challenges faced in REST API development, where faults may not only arise from code but also from API configurations and interactions.

@@

\subsection{Dataset Creation and Preparation}

To effectively assess the applicability of fault localization techniques to REST APIs, we will first develop a comprehensive dataset of REST API faults. This dataset will be mined from the GitHub repositories  that cover a wide range of REST API applications. 
The faults mined through these tests will be categorized based on a previously established taxonomy of REST API faults, ensuring that each fault type is adequately represented.

\subsection{Selection of Fault Localization Techniques}

The study will focus on three primary fault localization techniques that have shown promise in traditional software contexts but whose effectiveness in REST APIs remains underexplored:
\begin{enumerate}
    \item \textbf{Spectrum-Based Fault Localization (SBFL)}: We will use Jaguar, a tool that supports both control-flow and data-flow spectra, to identify potentially faulty code sections in REST API implementations.
    \item \textbf{Information Retrieval Fault Localization (IRFL)}: Techniques from this category will be applied using methods that analyze bug reports and code changes to align textual descriptions with code anomalies. We are planning on using tools like BLIA or BLUiR or BugLocator
    \item \textbf{Program Slicing}: This technique will be adapted to trace dependencies and potential fault propagation paths within REST API codebases, focusing on understanding how data flows across different API components affect the overall behavior. Tools like Soot, JavaSlicer are widely known for Program Slicing Fault Localization technique implementation as a tool.
\end{enumerate}

\subsection{Integration with REST API Characteristics}

Given the unique challenges posed by REST APIs, such as stateless operations and the presence of non-code artifacts (e.g., configuration files and API specifications), our approach will also consider these elements:
\begin{itemize}
    \item \textbf{Handling Stateless Nature}: We will simulate sequences of API calls to replicate typical client-server interactions and observe how faults manifest over such stateless communications.
    \item \textbf{Non-Code Artifacts}: Special attention will be given to faults that may originate from or affect non-code artifacts. We will explore methods to extend traditional fault localization techniques to recognize and diagnose issues stemming from incorrect configurations or erroneous API specifications.
\end{itemize}

@@

To conduct this research, a dataset is required for evaluation. The dataset contains REST API faults, their sources, and other relevant information necessary to evaluate FL techniques.

The dataset is mined using GitHub APIs from 15 different REST API repositories from Table ~\ref{tab:repositories},. The mining process filters out issues not marked as 'bugs' and 'closed,' leaving only the set of issues that have been fixed. Issues involving code changes are collected and then further filtered through manual analysis to select those applicable to this research.

\begin{table}[ht]
    \centering
    \caption{List of Repositories}
    \label{tab:repositories}
    \begin{tabular}{|c|l|}
    \hline
    \textbf{No.} & \textbf{Repository Name} \\ \hline
    1 & management-api-for-apache-cassandra \\ \hline
    2 & catwatch \\ \hline
    3 & cwa-verification-server \\ \hline
    4 & digdag \\ \hline
    5 & enviroCar-server \\ \hline
    6 & features-service \\ \hline
    7 & gravitee-api-management \\ \hline
    8 & kafka-rest \\ \hline
    9 & ocvn \\ \hline
    10 & ohsome-api \\ \hline
    11 & proxyprint-kitchen \\ \hline
    12 & quartz-manager \\ \hline
    13 & restcountries \\ \hline
    14 & senzing-api-server \\ \hline
    15 & Ur-Codebin-API \\ \hline
    \end{tabular}
    \end{table}

This dataset provide a benchmark to evaluate FL techniques on REST API faults.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\textwidth]{img1.png}
    \caption{Sample Out from mined repo}
    \label{fig:outputOfMine}
    \end{figure}

@@

There are several metrics that can be used to evaluate how effective FL techniques are at localizing REST API faults. In this research, two primary metrics to consider are \textbf{Top-k accuracy}, and \textbf{EXAM}.

     \textbf{Top-k accuracy:} This metric measures the percentage of faulty statements found within the top k positions of the ranking generated by an FL technique. The ranking positions are based on how likely each statement is considered faulty according to the fault localization algorithm. This metric is useful for evaluating how effective FL techniques are at localizing faults. In this research, several values of k are used to measure the FL technique's performance, such as top-1, top-3, top-5, and top-10.
    \\
    This metric measures the percentage of times the actual faulty statements are within the top $k$ positions of a ranked list produced by the fault localization technique. Mathematically, it is expressed as:
    \[
    \text{Top-k} = \frac{\text{ \#faults found in top } k \text{ positions}}{\text{Total number of faults}} \times 100\%
    \]
    This metric evaluates the effectiveness of fault localization techniques by their ability to rank the actual faulty statements highly on the list. Commonly used values for $k$ include 1, 3, 5, and 10.
    \\

    \textbf{EXAM score:}  This metric is defined as the percentage of the total statements a developer needs to examine before finding the fault location. A low EXAM score indicates that the fault localization technique was able to rank faulty statements highly, reducing the amount of code that needs to be inspected. This reflects an effective fault localization technique that quickly directs developers to the most likely faulty areas. However, the EXAM score does not account for multiple faults, limiting its ability to measure the effectiveness of an FL technique for multiple faults.

    The EXAM score is calculated as the percentage of the code that must be examined until the first occurrence of a fault is encountered. It is defined as:
    \\
    \[
    \text{EXAM Score} = \frac{\text{Position offault in the ranked list}}{\text{Total number of statements}} \times 100\%
    \]
    A lower EXAM score indicates a more effective fault localization technique, as it suggests that fewer statements need to be inspected before finding the fault. This metric is particularly useful for assessing the efficiency of a technique in directing developers quickly to the likely fault locations.
    \\ \\
    \textbf{Preicision}: This metric measures the fraction of actually faulty statements out of the total reported faulty statements. It provides a measurement indicating how well an FL technique can localize faults. However, it doesn't capture an FL technique's capability to localize all faults.
    \\

The metrics are effective measures of FL technique performance. They will be used to measure how well FL techniques can localize REST API faults.

@@

The objective of our experiments is to systematically evaluate the effectiveness of fault localization techniques on REST APIs. Below, we outline the structured procedure for executing these experiments.

\textbf{Setup}
For each REST API \( A \):
\begin{enumerate}
    \item Identify and enumerate all known faults \( F \) within the API.
    \item Select fault localization techniques \( T \) that are applicable to REST APIs. Each technique will be tested for its ability to accurately localize faults within the API.
\end{enumerate}

\textbf{Experimental Algorithm}
The following algorithm details the steps involved in evaluating each fault localization technique:

\section{Experimental Procedure}

The objective of our experiments is to systematically evaluate the effectiveness of fault localization techniques on REST APIs. Below, we outline the structured procedure for executing these experiments.

\subsection{Setup}
For each REST API \( A \):
\begin{itemize}
    \item Identify and enumerate all known faults \( F \) within the API.
    \item Select fault localization techniques \( T \) that are applicable to REST APIs. Each technique will be tested for its ability to accurately localize faults within the API.
\end{itemize}

\subsection{Experimental Algorithm}
The following algorithm details the steps involved in evaluating each fault localization technique, formatted to fit within a two-column document layout:

\begin{figure}[!h]
    \centering
    \caption{Evaluate Fault Localization Techniques}
    \begin{tabularx}{\columnwidth}{X}
    \textbf{for each} API \( A \) \textbf{do} \\
    \quad \textbf{for each} Fault \( F \) \textbf{in} \( A \) \textbf{do} \\
    \quad\quad \textbf{for each} Technique \( T \) \textbf{that supports} \( A \) \textbf{do} \\
    \quad\quad\quad \textit{Localize Fault:} \\
    \quad\quad\quad \( R \leftarrow \) localize(Fault \( F \), using \( T \)) \\
    \quad\quad\quad \( o/p \leftarrow \) compare(\( R \), GroundTruth) \\
    \quad\quad\quad \textbf{if} \( o/p \) \textbf{is true then} \\
    \quad\quad\quad\quad localize(Fault) \\
    \quad\quad\quad \textbf{else} \\
    \quad\quad\quad\quad unlocalize(Fault) \\
    \quad\quad\quad \textbf{end if} \\
    \quad\quad \textbf{end for} \\
    \quad \textbf{end for} \\
    \textbf{end for} \\

    Record the number of Faults localized and not localized
    \end{tabularx}
    \end{figure}

\textbf{Data Analysis}
    \begin{itemize}
        \item Aggregate data to calculate overall performance metrics.
        \item Analyze data to identify conditions under which each technique performs best.
    \end{itemize}

\textbf{Reporting Results}
The results of the experiments will be presented in a comparative format, highlighting the effectiveness of each technique, based on:
\begin{enumerate}
    \item Number of faults correctly localized versus not localized.
    \item Statistical analysis of performance metrics across different APIs and fault types.
    \item Discussion of technique-specific strengths or weaknesses observed during the experiments.
\end{enumerate}

@@

\bibliographystyle{IEEEtran}
\bibliography{relatedwork}
